Supplementary materials for: Modelling palaeoecological time series using generalized additive models

### 2018-08-15 supplementary-materials.Rmd
bump date

---
title: "Supplementary materials for: Modelling palaeoecological time series using generalized additive models"
author: Gavin L. Simpson
affiliation: "Institute of Environmental Change and Society, \\ University of Regina, Regina, Saskatchewan, Canada, S4S 0A2"
mail: "gavin.simpson@uregina.ca"
date: August 14, 2018
keywords: time series; generalized additive model; simultaneous interval; spline; environmental change 
bibliography: references.bib
csl: frontiers-in-ecology-and-evolution.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
fontsize: 12pt
mainfont: TeX Gyre Pagella
output:
  pdf_document:
    highlight: tango
    number_sections: true
    fig_width: 8
    fig_height: 5
    fig_crop: false
    keep_tex: true
    latex_engine: xelatex
    md_extensions: +header_attributes+superscript+subscript
    includes:
      in_header: header.tex
  md_document:
    variant: markdown_github
---

>>>>

---
title: "Supplementary materials for: Modelling palaeoecological time series using generalized additive models"
author: Gavin L. Simpson
affiliation: "Institute of Environmental Change and Society, \\ University of Regina, Regina, Saskatchewan, Canada, S4S 0A2"
mail: "gavin.simpson@uregina.ca"
date: August 15, 2018
keywords: time series; generalized additive model; simultaneous interval; spline; environmental change 
bibliography: references.bib
csl: frontiers-in-ecology-and-evolution.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
fontsize: 12pt
mainfont: TeX Gyre Pagella
output:
  pdf_document:
    highlight: tango
    number_sections: true
    fig_width: 8
    fig_height: 5
    fig_crop: false
    keep_tex: true
    latex_engine: xelatex
    md_extensions: +header_attributes+superscript+subscript
    includes:
      in_header: header.tex
  md_document:
    variant: markdown_github
---
